### 2019-12-17 paper/conclusion.tex
After Andrei's comments in Title, Abstract and Intro #4

Five different absorber materials are considered based on their neutronics and 
safety performance: B$_4$C-90 (boron is enriched to 90\% $^{10}$B), HfB$_2$, 
HfH$_{1.62}$, Eu$_2$O$_3$, and Gd$_2$O$_3$. Enriched B$_4$C-90 has the largest 
absorption ability, while Gd$_2$O$_3$ has the lowest absorption compared with 
the other absorber materials in this study. Both CSD and SSD clusters are 
separately able to shut down the reactor initially loaded with $^{233}$U and 
reactor-grade Pu regardless of the absorber material type. However, only SSD 
clusters made of B$_4$C-90 is able to shut down the SD-TMSR initially loaded 
with transuranium vector from \gls{LWR}. The reason for this is much larger 
absorption cross section of $^{10}$B in the relatively soft neutron energy 
spectrum of the SD-TMSR core started with TRU.

@@

All absorber materials provide an adequate shutdown margin for the SD-TMSR 
core that initially loaded with $^{233}$U and reactor-grade Pu. However, the 
shutdown margins for TRU case are negative or slightly positive (in B$_4$C-90 
case), this makes the SSD clusters ineffective to shut down the reactor loaded 
with TRU.

@@

The integral and differential control rod worth are calculated for three 
different systems: all control rods, CSD, and SSD systems. The results show 
that all absorber materials have almost the same integral rod worth in the 
upper half of the core. Further insertion of the control rods shows the unique 
absorption characteristics of each material.

>>>>

Five different absorbing materials are considered based on their neutronics and 
safety performance: B$_4$C-90 (boron is enriched to 90\% $^{10}$B), HfB$_2$, 
HfH$_{1.62}$, Eu$_2$O$_3$, and Gd$_2$O$_3$. Enriched B$_4$C-90 has the largest 
absorption ability, while Gd$_2$O$_3$ has the lowest absorption compared with 
the other absorbing materials in this study. Both CSD and SSD clusters are 
separately able to shut down the reactor initially loaded with $^{233}$U and 
reactor-grade Pu regardless of the absorbing material type. However, only SSD 
clusters made of B$_4$C-90 is able to shut down the SD-TMSR initially loaded 
with transuranium vector from \gls{LWR}. The reason for this is much larger 
absorption cross section of $^{10}$B in the relatively soft neutron energy 
spectrum of the SD-TMSR core started with TRU.

@@

All absorbing materials provide an adequate shutdown margin for the SD-TMSR 
core that initially loaded with $^{233}$U and reactor-grade Pu. However, the 
shutdown margins for TRU case are negative or slightly positive (in B$_4$C-90 
case), this makes the SSD clusters ineffective to shut down the reactor loaded 
with TRU.

@@

The integral and differential control rod worth are calculated for three 
different systems: all control rods, CSD, and SSD systems. The results show 
that all absorbing materials have almost the same integral rod worth in the 
upper half of the core. Further insertion of the control rods shows the unique 
absorption characteristics of each material.

### 2019-12-17 paper/introduction.tex
After Andrei's comments in Title, Abstract and Intro #4

The \gls{GIF} \cite{doe2002technology} determined six innovative reactor 
systems: the Very High-Temperature Reactor (VHTR), the \gls{MSR}, the 
Supercritical Water-Cooled Reactor (SWCR), the Gas-cooled Fast Reactor (GFR), 
the Sodium-cooled Fast Reactor (SFR), and the Lead-cooled Fast Reactor (LFR). 
The MSR is the only liquid-fueled reactor among these reactors. Major nuclear 
centers pursue MSRs with renewed interest \cite{betzler_impacts_2019, 
ashraf2019whole_core,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity}.
 The MSR is a promising technology because of its dynamics, especially for 
thorium fuel utilization. However, this technology has difficulties in safety, 
online reprocessing, and fuel handling. Safety is one of the primary goals of 
the MSR systems, which was understudied and require further investigation. The 
unique characteristics of the MSRs (liquid fuel, flux level, neutron economy, 
etc.) strongly affect its control system design. Graphite-moderated MSRs have 
a negative total temperature coefficient of reactivity 
\cite{robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,ashraf2019whole_core}.
 Doppler effect and thermal expansion of the fuel reduce core reactivity when 
the core heats up. However, temperature coefficient of reactivity for graphite 
is small but positive due to Doppler effect \cite{mathieu2006thorium, 
rykhlevskii_full-core_2017}. The graphite expansion is not a 
dominating factor, thus core reactivity will decrease automatically when the 
core heats up \cite{li_optimization_2018}. MSR designs have a drain tanks to 
hold and cool down the liquid fuel in an emergency case. A freeze plug, which 
located under the core, passively melts when the fuel temperature reaches a 
critical point, and drains the fuel salt from the reactor vessel to the drain 
tanks. The drain tanks have a subcritical
configuration with a large free 
surface area to readily dissipate heat by passive cooling 
\cite{elsheikh2013safety}.

Safety aspects in the MSRs can be listed as follows 
\cite{elsheikh2013safety,merle2008optimization}:
\begin{enumerate}
\item The negative coefficient of reactivity - high core temperature will reduce reactivity.
\item The fuel feed rate - decreasing the refueling rate slows down and eventually stops the nuclear chain reaction.
\item The drain tanks, which have subcritical geometry and passively cooled.
\item The control rods compensate the excess reactivity, regulate temperature, and/or shut down the reactor.
\item The continuous removing of fission products and radioactive gasses minimize the chance of radiation exposure.
\item The outer containment vessel.
\end{enumerate}

At the Beginning of Life (BOL), we must load the MSR with larger amount of 
fuel than that required to achieve criticality (necessary for long term core 
operation). This leads to excess reactivity at the BOL 
\cite{duderstadt650nuclear}. Additionally, during burnup, the online 
reprocessing and refueling leads to slow reactivity change, which 
should be compensated \cite{ashraf2019whole_core}. The most common procedure 
for reactor control is to insert or withdraw control rods made of material 
with large neutron absorption cross section (e.g., boron, cadmium) 
\cite{duderstadt650nuclear}. 
Insertion of control rods introduces an amount of negative reactivity into the 
core. This negative reactivity helps to compensate the excess reactivity and 
adjust the power level of the core or shut down the reactor in case of  
emergency \cite{glasstone1967nuclear}. Therefore, we should estimate 
the reactivity worth of the control rods 
\cite{varvayanni2009estimation,fadaei2009control,aoyama2007core,bretscher1997computing}.
 The reactivity worth of control rods correlates with the interference 
(shadowing effects) between control rod clusters 
\cite{girardin2008development,vcerba2017optimization}. 
The control rod worth and its efficiency to absorb excess positive reactivity is a subject of major interest since it directly affects reactor safety \cite{liu2018criticality,atkinson2019small,vcerba2017optimization,do2019criticality,guo2019advanced,varvayanni2009estimation}.

Boron carbide (B$_4$C) is commonly used material for the control rods 
\cite{zhong2019preliminary,steinbruck2010degradation,dunner1984absorber}. 
However, we may need to enrich the boron isotope ($^{10}$B) to reach 
the necessary absorption cross section. Notably, the spatial self-shielding 
effect correlates with $^{10}$B concentration. For example, B$_4$C enriched to 
90\% contains $^{10}$B 4.5 times larger than in natural B$_4$C, however, its 
absorption ability is about 2.3 times compared with natural B$_4$C. 
Additionally, issues related to helium gas release, swelling, melting risk, 
and high loss of the reactivity worth limit the B$_4$C lifespan 
\cite{guo2019optimized}.

Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the 
potential alternative absorbers for Generation-IV reactors such as 
hafnium-based materials and rare earth element oxides. These absorbers have 
high thermal conductivity, good resistance to neutron irradiation, and release 
almost no gas 
\cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.

The \gls{SD-TMSR} with a thermal power of 2,250 MW$_{th}$ 
\cite{ashraf2019whole_core,li_optimization_2018} is a graphite-moderated 
molten salt reactor. Recent studies on MSRs showed that the excess reactivity 
at the beginning of the operation is quite large for many refueling scenarios 
\cite{ashraf2019whole_core,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}.
 Adjusting fertile and fissile feed rates helps to control the reactivity of 
the SD-TMSR \cite{ashraf2019whole_core}. However, we should introduce a 
reliable safety system beside the online feed system to control the excess 
reactivity. Therefore, the main objective of our study is to introduce a new 
fast reactivity control based on control rods in the \gls{SD-TMSR} to control 
the reactivity during normal operation. Five different absorber materials are 
applied to study the main neutronics and safety parameters in the SD-TMSR. We 
focus on the control rod design, absorption ability, integral and differential 
control rod worths, shutdown margin of absorber materials, and shadowing 
effects at steady state calculation.

>>>>

The \gls{GIF} \cite{doe2002technology} determined six innovative reactor 
systems: the Very High-Temperature Reactor (VHTR), the \gls{MSR}, the 
Supercritical Water-Cooled Reactor (SWCR), the Gas-cooled Fast Reactor (GFR), 
the Sodium-cooled Fast Reactor (SFR), and the Lead-cooled Fast Reactor (LFR). 
The MSR is the only liquid-fueled reactor among these reactors. Major nuclear 
centers pursue MSRs with renewed interest \cite{betzler_impacts_2019, 
ashraf2019whole_core,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity}.
The MSR is a promising technology because of its dynamics, especially for 
thorium fuel utilization. However, this technology has difficulties in safety, 
online reprocessing, and fuel handling. Safety is one of the primary goals of 
the MSR systems, which was understudied and require further investigation. The 
unique characteristics of the MSRs (liquid fuel, flux level, neutron economy, 
etc.) strongly affect its control system design. Graphite-moderated MSRs have 
a negative total temperature coefficient of reactivity 
\cite{ashraf2019whole_core,robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,li_optimization_2018}.
Doppler effect and thermal expansion of the fuel reduce core reactivity when 
the core heats up. MSR designs have a drain tanks to 
hold and cool down the liquid fuel in an emergency case. A freeze plug, which 
located under the core, passively melts when the fuel temperature reaches a 
critical point, and drains the fuel salt from the reactor vessel to the drain 
tanks. The drain tanks have a subcritical
configuration with a large free 
surface area to readily dissipate heat by passive cooling 
\cite{elsheikh2013safety}.

At the Beginning of Life (BOL), the MSR is commonly load with larger amount of 
fuel than that required to achieve criticality (necessary for long term core 
operation). This leads to excess reactivity at the BOL. Recent studies on MSRs showed that this excess reactivity 
at the BOL is quite large for many refueling scenarios 
\cite{ashraf2020Strategies,ashraf2019whole_core,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}.
Additionally, during burnup, the online 
reprocessing and refueling leads to slow reactivity change, which 
should be compensated \cite{ashraf2020Strategies,ashraf2019whole_core}. 
The online reprocessing and refueling system helps to control the reactivity of 
the MSRs \cite{ashraf2019whole_core}. However, the most common and reliable procedure 
for reactor control is to insert or withdraw control rods made of material 
with large neutron absorption cross section (e.g., boron, cadmium) 
\cite{duderstadt650nuclear}. 
Insertion of control rods introduces an amount of negative reactivity into the 
core. This negative reactivity helps to compensate the excess reactivity and 
adjust the power level of the core or shut down the reactor in case of  
emergency \cite{glasstone1967nuclear}. Therefore, we should estimate 
the reactivity worth of the control rods 
\cite{varvayanni2009estimation,fadaei2009control,aoyama2007core,bretscher1997computing}.
 The reactivity worth of control rods correlates with the interference 
(shadowing effects) between control rod clusters 
\cite{girardin2008development,vcerba2017optimization}. 
The control rod worth and its efficiency to absorb excess positive reactivity is a subject of major interest since it directly affects reactor safety \cite{liu2018criticality,atkinson2019small,vcerba2017optimization,do2019criticality,guo2019advanced,varvayanni2009estimation}.

Boron carbide (B$_4$C) is commonly used material for the control rods 
\cite{zhong2019preliminary,steinbruck2010degradation,dunner1984absorber}. 
However, we may need to enrich the boron isotope ($^{10}$B) to reach 
the necessary absorption cross section. Additionally, issues related to helium gas release, swelling,
and high loss of the reactivity worth limit the B$_4$C lifespan 
\cite{guo2019optimized}. Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the 
potential alternative absorbers for Generation-IV reactors such as 
hafnium-based materials and rare earth element oxides. These absorbers have 
high thermal conductivity, good resistance to neutron irradiation, and release 
almost no gas 
\cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.

The \gls{SD-TMSR} with a thermal power of 2,250 MW$_{th}$ 
\cite{ashraf2019whole_core,li_optimization_2018} is a graphite-moderated 
molten salt reactor. Adjusting fertile and fissile feed rates helps to control the reactivity of 
the SD-TMSR \cite{ashraf2019whole_core,ashraf2020Strategies,li_optimization_2018}. However, reactivity control system for maneuvering and emergency shutdown was not introduced in the literature \cite{li_optimization_2018,zou2018transition,zhang2020radiotoxicity,jiang2012advanced,zou2018preliminary,ZOU2015114}. Therefore, the main objective of our study is to introduce a new 
fast reactivity control system based on control rods in the \gls{SD-TMSR} to control 
the reactivity during normal operation and shut down the reactor in case of  
emergency. Five different absorbing materials are 
applied to study the main neutronics and safety parameters in the SD-TMSR. We 
focus on the control rod design, absorption ability, integral and differential 
control rod worths, shutdown margin of absorbing materials, and shadowing 
effects at steady state calculation.

### 2019-12-17 paper/methods.tex
After Andrei's comments in Title, Abstract and Intro #4

The reactivity of the SD-TMSR core is controlled by two clusters of control 
rods:
\begin{enumerate}
\item Control Safety Devices (CSD);
\item Shutdown Safety Devices (SSD).
\end{enumerate}
The CSD system is designed for reactivity control during normal operation and the SSD system is designed for an emergency reactor shutdown.
In the present work, five different absorber materials are considered based on their neutronics and safety performance:
\begin{enumerate}
\item B$_4$C with boron enriched to 90\% $^{10}$B;
\item hafnium diboride (HfB$_2$);
\item hafnium hydride (HfH$_{1.62}$);
\item gadolinium oxide (Gd$_2$O$_3$);
\item europium oxide (Eu$_2$O$_3$).
\end{enumerate}
Boron carbide (B$_4$C) is widely used in control rods fabrication. Enriching 
PB$_4$C increases the fraction of highly neutron absorber isotope (i.e. 
$^{10}$B) and helps to reach the necessary absorptivity. However, issues 
related to helium gas release through (n,$\alpha$) reactions of $^{10}$B, 
swelling, melting risk, and high loss of the reactivity worth limit the B$_4$C 
lifespan \cite{guo2019optimized}. Hafnium and rare earth elements oxides 
absorb neutrons through (n,$\gamma$) reactions and this limits gas emission.

The control rod is a cylinder with a radius of 0.75 cm and a height of 520 cm. 
The absorber material is surrounded by a 0.25-cm-thick cladding made of AIM1 
(15Cr-15Ni) steel alloy \cite{SERAN2017285} and the rod follower is made of 
SiC structural material (see Figure~\ref{fig:cr}). A small gap between the 
cladding and rod follower is considered to facilitate the control rod movement.

>>>>

The reactivity of the SD-TMSR core is controlled by two clusters of control 
rods:
\begin{enumerate}
\item Control Safety Devices (CSD);
\item Shutdown Safety Devices (SSD).
\end{enumerate}
The CSD system is designed for reactivity control during normal operation and the SSD system is designed for an emergency reactor shutdown.
In the present work, five different absorbing materials are considered based on their neutronics and safety performance:
\begin{enumerate}
\item B$_4$C with boron enriched to 90\% $^{10}$B;
\item hafnium diboride (HfB$_2$);
\item hafnium hydride (HfH$_{1.62}$);
\item gadolinium oxide (Gd$_2$O$_3$);
\item europium oxide (Eu$_2$O$_3$).
\end{enumerate}
Boron carbide (B$_4$C) is widely used in control rods fabrication. Enriching 
PB$_4$C increases the fraction of highly neutron absorber isotope (i.e. 
$^{10}$B) and helps to reach the necessary absorptivity. However, issues 
related to helium gas release through (n,$\alpha$) reactions of $^{10}$B, 
swelling, melting risk, and high loss of the reactivity worth limit the B$_4$C 
lifespan \cite{guo2019optimized}. Hafnium and rare earth elements oxides 
absorb neutrons through (n,$\gamma$) reactions and this limits gas emission.

The control rod is a cylinder with a radius of 0.75 cm and a height of 520 cm. 
The absorbing material is surrounded by a 0.25-cm-thick cladding made of AIM1 
(15Cr-15Ni) steel alloy \cite{SERAN2017285} and the rod follower is made of 
SiC structural material (see Figure~\ref{fig:cr}). A small gap between the 
cladding and rod follower is considered to facilitate the control rod movement.

### 2019-12-17 paper/results.tex
After Andrei's comments in Title, Abstract and Intro #4

The control rod parameters including control rod worth (CRW), interference 
between CR clusters, and integral and differential control rod worths are 
described in this part. Five different absorber materials are considered based 
on their neutronics and safety performance (see part \ref{CRD}). 
Table~\ref{tab:worth} shows calculated control rod worth, the amplification 
factor (A$_{CRi}$), and the type of interference for five different 
absorbers.

@@

The total worth of all control rods ranges from $33.7\pm0.4$ to $48.19\pm0.68$ 
\$ (Table~\ref{tab:worth}). B$_4$C-90 (boron is enriched to 90\% $^{10}$B) 
has the largest absorption ability, while Gd$_2$O$_3$ has the lowest 
absorption compared with the other absorber materials in this study. This 
result agrees with macroscopic absorption cross sections data 
\cite{guo2019optimized}. B$_4$C-90 has the highest macroscopic 
absorption cross sections followed by Eu$_2$O$_3$, HfB$_2$, HfH$_{1.62}$, and 
finally Gd$_2$O$_3$. The control rod material are being transmuted during 
operation. The effect of the fuel salt burnup on the control rod worth is not 
considered herein, and will be investigated and presented in Part II of this 
study.

Additionally, the worth of the CSD clusters is by factor $1.56$ greater than 
the worth of the SSD system for all absorber materials. Either CSD or SSD 
clusters are able to shut down the reactor initially loaded by 
$^{233}$U and reactor-grade Pu regardless of the absorber material type. 
However, only SSD clusters made of B$_4$C-90 are able to shut down the SD-TMSR 
initially loaded with transuranic (TRU) elements. Increasing the number of SSD 
cluster or changing their location would increase the worth.

The inner ring of the CSD is located in the central zone of the SD-TMSR core 
(Figure~\ref{fig:core_25}), where the volume ratio between molten salt and 
graphite is $0.357$. Results show that the inner ring of the CSD has 
the worth almost equal to the worth of all other CRs together regardless of 
the absorber material type (Table~\ref{tab:worth}). This may be attributed to 
the fact that the absorption cross section decreases with the energy of 
incident neutron, for example, boron absorbs neutrons in thermal spectrum much 
greater than in fast spectrum.

@@

The SSD clusters are designed mainly for an emergency shutdown, thus it should 
provide the reactor core with sufficient and adequate negative reactivity. The 
shutdown margin (SDM) is calculated by equation~\ref{Equ:6}.  
Table~\ref{tab:table2} summarizes the shutdown margins for the SD-TMSR core 
initially loaded with $^{233}$U,  reactor-grade Pu, and transuranic (TRU) 
elements for different absorber materials. All absorber materials provide an 
adequate shutdown margin for the SD-TMSR core that initially loaded with 
$^{233}$U and reactor-grade Pu. However, the shutdown margins for TRU case are 
negative or slightly positive (in B$_4$C-90 case), this makes the SSD clusters 
ineffective to shut down the reactor loaded with TRU.
\begin{table}  [!hb]
	\caption{The shutdown margins for the SD-TMSR core for different absorber materials.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{3cm} s s s}
		\hline
		Absorber materials        				&  $^{233}$U & reactor-grade Pu&  TRU \\
		\hline
		B$_4$C-90                          & $14.74\pm0.09$ $\$$ & $12.28\pm0.12$ $\$$ &$1.01\pm0.09$ $\$$ \\
		Eu$_2$O$_3$                       &  $12.93\pm0.09$ $\$$    &  $10.47\pm0.12$ $\$$   &$-0.8\pm0.09$ $\$$\\
		HfB$_2$        				 &$12.62\pm0.24$ $\$$ &$10.16\pm0.26$ $\$$ &$-1.11\pm0.24$ $\$$   \\
		HfH$_{1.62}$							& $11.58\pm0.19$ $\$$ &$9.12\pm0.22$ $\$$ &$-2.15\pm0.19$ $\$$ \\
		Gd$_2$O$_3$	  		& $10.35\pm0.22$ $\$$ &$7.89\pm0.25$ $\$$& $-3.38\pm0.22$ $\$$\\
		\hline
	\end{tabularx}
	\label{tab:table2}
\end{table}

@@

Insertion of the control rod affects the neutron flux distribution, which is 
the primary reason for the amplification of CR worths indicated in 
Table~\ref{tab:worth}. Figure~\ref{fig:totalflux} illustrates the radial 
neutron flux distribution at the mid-core level with different CRs position: 
(1) all CRs withdrawn, (2) all CRs inserted, (3) all CSD inserted, (4) all SSD 
inserted. We chose the B$_4$C-90 as absorber materials because of its high 
absorption ability. As shown in Figure~\ref{fig:totalflux}, the insertion of 
CRs deforms the radial flux shape in certain positions, i.e., around CRs 
positions. This shifts the neutron flux from the core center towards the 
periphery. The maximum neutron flux shift occurs when all CRs are inserted 
into the core.
\begin{figure}[!ht]
	\centering
	\includegraphics[width=\textwidth]{totalflux.png}
	\vspace{-0.5in}
	\caption{Radial neutron flux distribution at the mid-core for different 
	CRs positions.} 
	\label{fig:totalflux}
\end{figure}

@@

Figure~\ref{fig:CSD} shows the integral CRW for only CSD clusters with five 
different absorber materials. The results show that all absorber materials 
have almost the same integral rod worth in the upper quarter of the core 
($<130$cm from the upper boundary of the core). Further insertion of the 
control rods shows the unique absorption characteristics of each material (see 
part~\ref{CR_worth}). B$_4$C-90 absorbs much more neutrons than the 
Gd$_2$O$_3$, which has the lowest absorption ability among the other absorber 
materials in this study. All result are based on steady state calculations. 
Further and detailed analysis including burnup calculation will be represented 
in the near future.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{integ.png}
	\vspace{-0.5in}
	\caption{Integral control rod worth of all CRs, CSD, and SSD clusters.} 
	\label{fig:integ}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{diff.png}
	\vspace{-0.5in}
	\caption{Differential control rod worth of all CRs, CSD, and SSD clusters.} 
	\label{fig:diff}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{CSD.png}
	\vspace{-0.5in}
	\caption{Integral control rod worth of CSD clusters for different absorber materials.} 
	\label{fig:CSD}
\end{figure}

>>>>

The control rod parameters including control rod worth (CRW), interference 
between CR clusters, and integral and differential control rod worths are 
described in this part. Five different absorbing materials are considered based 
on their neutronics and safety performance (see part \ref{CRD}). 
Table~\ref{tab:worth} shows calculated control rod worth, the amplification 
factor (A$_{CRi}$), and the type of interference for five different 
absorbers.

@@

The total worth of all control rods ranges from $33.7\pm0.4$ to $48.19\pm0.68$ 
\$ (Table~\ref{tab:worth}). B$_4$C-90 (boron is enriched to 90\% $^{10}$B) 
has the largest absorption ability, while Gd$_2$O$_3$ has the lowest 
absorption compared with the other absorbing materials in this study. This 
result agrees with macroscopic absorption cross sections data 
\cite{guo2019optimized}. B$_4$C-90 has the highest macroscopic 
absorption cross sections followed by Eu$_2$O$_3$, HfB$_2$, HfH$_{1.62}$, and 
finally Gd$_2$O$_3$. The control rod material are being transmuted during 
operation. The effect of the fuel salt burnup on the control rod worth is not 
considered herein, and will be investigated and presented in Part II of this 
study.

Additionally, the worth of the CSD clusters is by factor $1.56$ greater than 
the worth of the SSD system for all absorbing materials. Either CSD or SSD 
clusters are able to shut down the reactor initially loaded by 
$^{233}$U and reactor-grade Pu regardless of the absorbing material type. 
However, only SSD clusters made of B$_4$C-90 are able to shut down the SD-TMSR 
initially loaded with transuranic (TRU) elements. Increasing the number of SSD 
cluster or changing their location would increase the worth.

The inner ring of the CSD is located in the central zone of the SD-TMSR core 
(Figure~\ref{fig:core_25}), where the volume ratio between molten salt and 
graphite is $0.357$. Results show that the inner ring of the CSD has 
the worth almost equal to the worth of all other CRs together regardless of 
the absorbing material type (Table~\ref{tab:worth}). This may be attributed to 
the fact that the absorption cross section decreases with the energy of 
incident neutron, for example, boron absorbs neutrons in thermal spectrum much 
greater than in fast spectrum.

@@

The SSD clusters are designed mainly for an emergency shutdown, thus it should 
provide the reactor core with sufficient and adequate negative reactivity. The 
shutdown margin (SDM) is calculated by equation~\ref{Equ:6}.  
Table~\ref{tab:table2} summarizes the shutdown margins for the SD-TMSR core 
initially loaded with $^{233}$U,  reactor-grade Pu, and transuranic (TRU) 
elements for different absorbing materials. All absorbing materials provide an 
adequate shutdown margin for the SD-TMSR core that initially loaded with 
$^{233}$U and reactor-grade Pu. However, the shutdown margins for TRU case are 
negative or slightly positive (in B$_4$C-90 case), this makes the SSD clusters 
ineffective to shut down the reactor loaded with TRU.
\begin{table}  [!hb]
	\caption{The shutdown margins for the SD-TMSR core for different absorbing materials.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{3cm} s s s}
		\hline
		Absorbing materials        				&  $^{233}$U & reactor-grade Pu&  TRU \\
		\hline
		B$_4$C-90                          & $14.74\pm0.09$ $\$$ & $12.28\pm0.12$ $\$$ &$1.01\pm0.09$ $\$$ \\
		Eu$_2$O$_3$                       &  $12.93\pm0.09$ $\$$    &  $10.47\pm0.12$ $\$$   &$-0.8\pm0.09$ $\$$\\
		HfB$_2$        				 &$12.62\pm0.24$ $\$$ &$10.16\pm0.26$ $\$$ &$-1.11\pm0.24$ $\$$   \\
		HfH$_{1.62}$							& $11.58\pm0.19$ $\$$ &$9.12\pm0.22$ $\$$ &$-2.15\pm0.19$ $\$$ \\
		Gd$_2$O$_3$	  		& $10.35\pm0.22$ $\$$ &$7.89\pm0.25$ $\$$& $-3.38\pm0.22$ $\$$\\
		\hline
	\end{tabularx}
	\label{tab:table2}
\end{table}

@@

Insertion of the control rod affects the neutron flux distribution, which is 
the primary reason for the amplification of CR worths indicated in 
Table~\ref{tab:worth}. Figure~\ref{fig:totalflux} illustrates the radial 
neutron flux distribution at the mid-core level with different CRs position: 
(1) all CRs withdrawn, (2) all CRs inserted, (3) all CSD inserted, (4) all SSD 
inserted. We chose the B$_4$C-90 as absorbing materials because of its high 
absorption ability. As shown in Figure~\ref{fig:totalflux}, the insertion of 
CRs deforms the radial flux shape in certain positions, i.e., around CRs 
positions. This shifts the neutron flux from the core center towards the 
periphery. The maximum neutron flux shift occurs when all CRs are inserted 
into the core.
\begin{figure}[!ht]
	\centering
	\includegraphics[width=\textwidth]{totalflux.png}
	\vspace{-0.5in}
	\caption{Radial neutron flux distribution at the mid-core for different 
	CRs positions.} 
	\label{fig:totalflux}
\end{figure}

@@

Figure~\ref{fig:CSD} shows the integral CRW for only CSD clusters with five 
different absorbing materials. The results show that all absorbing materials 
have almost the same integral rod worth in the upper quarter of the core 
($<130$cm from the upper boundary of the core). Further insertion of the 
control rods shows the unique absorption characteristics of each material (see 
part~\ref{CR_worth}). B$_4$C-90 absorbs much more neutrons than the 
Gd$_2$O$_3$, which has the lowest absorption ability among the other absorbing 
materials in this study. All result are based on steady state calculations. 
Further and detailed analysis including burnup calculation will be represented 
in the near future.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{integ.png}
	\vspace{-0.5in}
	\caption{Integral control rod worth of all CRs, CSD, and SSD clusters.} 
	\label{fig:integ}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{diff.png}
	\vspace{-0.5in}
	\caption{Differential control rod worth of all CRs, CSD, and SSD clusters.} 
	\label{fig:diff}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{CSD.png}
	\vspace{-0.5in}
	\caption{Integral control rod worth of CSD clusters for different absorbing materials.} 
	\label{fig:CSD}
\end{figure}
